Exploring Design Space for Differentially Private Bayesian Inference

### 2018-12-29 ICML2019/main.tex
update experiments

\begin{figure}[ht]
\begin{center}
\centering
\subfigure[Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$]
{ \includegraphics[width=0.4\textwidth]{sampling_2d.eps}
\label{fig_vs_datasize_2d}
}

\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
  \includegraphics[width=0.4\textwidth]{sampling_3d.eps} 
  \label{fig_vs_datasize_3d}
}
\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
  \includegraphics[width=0.4\textwidth]{sampling_4d.eps} 
  \label{fig_vs_datasize_4d}
}
\end{center}
\end{figure}

In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
of observations. The results show that when the data size increases, the average errors of
$\hexpmech$, Laplace mechanism and decrease. For small datasets,
i.e with size less $300$ in the case of Beta-Binomial models,
both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
we considered data sets of the order of 15 thousands elements,
the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).

\paragraph{Fixed dataset varying balanced priors}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ . We studied the accuracy under different priors, where the priors considered  are also balanced.
Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{sampling_prior.eps}
\caption{Observed data set is: $(50,50)$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.48\textwidth]{privacyloss.eps}
\caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
\label{fig_privacy}
\end{center}
\end{figure}

>>>>

\begin{figure}[ht]
\begin{center}
\centering
\subfigure[Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$]
{ \includegraphics[width=0.35\textwidth]{sampling_2d.eps}
\label{fig_vs_datasize_2d}
}

\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
  \includegraphics[width=0.35\textwidth]{sampling_3d.eps} 
  \label{fig_vs_datasize_3d}
}
\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
  \includegraphics[width=0.35\textwidth]{sampling_4d.eps} 
  \label{fig_vs_datasize_4d}
}
\end{center}
\end{figure}

In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
of observations. The results show that when the data size increases, the average errors of
$\hexpmech$, $\lapmech$ and $\ilapmech$ decrease. For small datasets,
i.e with size less $300$ in the case of Beta-Binomial models, the Laplace mechanisms outperform $\hexpmech$.
But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
we considered data sets of the order of 15 thousands elements,
the $\hexpmech$ outperforms the $\lapmech$, and asymptotically approaches the improved Laplace mechanism $\ilapmech$.
Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).

\paragraph{Fixed dataset varying balanced priors}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the data set to be $(50,50)$, and the parameters the same as before: $\epsilon = 1.0$ and $\delta = 10^{-8}$ . We studied the accuracy under different priors, where the priors considered  are also balanced.
Similar to the plots above, Figure \ref{fig_vs_prior} shows that in the beginning the baseline Laplace mechanism and improved Laplace mechanism performs better but the baseline approach is outperformed after a while, and very close to the improved Laplace mechanism.
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{sampling_prior.eps}
\caption{Observed data set is: $(50,50)$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.35\textwidth]{privacyloss.eps}
\caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
\label{fig_privacy}
\end{center}
\end{figure}
